Online Verification of Commutativity

### 2020-09-09 acmPaper/paper.tex
Kill an orphan
Little fixes

\begin{proof}
    Every element in the output of the path extraction algorithm was by construction an element of $O$.

    It is also clear that every cycle in $C'$ can be expressed as $(S, T) ; p$, and corresponds to the input two flip tolerant path p.

@@

\begin{algorithm}
\label{alg_spanning_set}
\DontPrintSemicolon
\KwResult{Find a spanning set Rs = [$r_1$, ... ,$r_k$].}

@@

\caption{finding spanning set}\label{algo_spanning_set}
\end{algorithm}

@@

\caption{Minimal spanning set}\label{algo_minimal_spanning_set}
\end{algorithm}

@@

\section{Evaluation}
\label{sec:evaluation}
We compare performance of the following path checking algorithms:
(1) the na\"{i}ve baseline,
(2) the less na\"{i}ve two-flip baseline,
(3) the batch baseline,
(4) \ref{algo_online_polynomial}, the non-minimal polynomial-time algorithm, and
(5) \ref{algo_online_minimal}, the minimal set finding algorithm.
The two metrics we evaluate are time for response and size of response set (smaller sets---tighter output results---would mean less calls to the oracle).
We use randomly generated graphs of varying size: given a graph and a new edge, we time how long it takes for an algorithm to return the set of pairs that need to be verified.
All computations were performed on a Macbook Pro 2015, 2.9 GHz Dual-Core Intel Core i5.

@@

\begin{table}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds of computation \\
    \hline
    Na\"{i}ve baseline & 0.77 \\
    Two Flip tolerant & 0.075 \\
    Batch algorithm & 7.55 \\
    ~\ref{algo_online_polynomial} & 0.0038 \\
    ~\ref{algo_online_minimal} & 0.00086 \\
    \hline
\end{tabular}
\caption{Computation time for 9 node graph of density 0.4, averaged over ten runs}
\label{tab:times} %TODO debug and fix label not working.
\end{table}

>>>>

\begin{proof}
    Every element in the output of the path extraction algorithm was by construction an element of $O$. Every cycle in $C'$ can be expressed as $(S, T) ; p$, and corresponds to the input two flip tolerant path $p$.

@@

\begin{algorithm}[t]
\label{alg_spanning_set}
\DontPrintSemicolon
\KwResult{Find a spanning set Rs = [$r_1$, ... ,$r_k$].}

@@

\caption{Finding a spanning set.}\label{algo_spanning_set}
\end{algorithm}

@@

\caption{Finding a minimal spanning set.}\label{algo_minimal_spanning_set}
\end{algorithm}

@@

\section{Evaluation}
\label{sec:evaluation}
We compare performance of the following path checking algorithms:
(1) the na\"{i}ve baseline,
(2) the less na\"{i}ve two-flip baseline,
(3) the batch baseline,
(4) \ref{algo_online_polynomial}, the non-minimal polynomial-time algorithm, and
(5) \ref{algo_online_minimal}, the minimal set finding algorithm.
The two metrics we evaluate are time for response and size of response set (smaller sets---tighter output results---would mean less calls to the oracle).
We use randomly generated graphs of varying size: given a graph and a new edge, we time how long it takes for an algorithm to return the set of pairs that need to be verified.
All computations were performed on a MacBook Pro 2015, 2.9 GHz dual-core Intel Core i5.

@@

\begin{table}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds of computation \\
    \hline
    Na\"{i}ve baseline & 0.77 \\
    Two Flip tolerant & 0.075 \\
    Batch algorithm & 7.55 \\
    ~\ref{algo_online_polynomial} & 0.0038 \\
    ~\ref{algo_online_minimal} & 0.00086 \\
    \hline
\end{tabular}
\caption{Computation time for 9-node graph of density 0.4, averaged over ten runs.}
\label{tab:times} %TODO debug and fix label not working.
\end{table}
